### 2021-06-10 paper/appendix_data.tex
Fill in some numbers and references on policies, seasonality and from the simulation results.

% seasonality
Another important factor in the potential for a contact to lead to an infection is the
seasonality.\comment[id=K]{Reference missing} There are two channels through which
seasonality affects the infectiousness of contacts. One has to do with the physical
conditions like UV radiation and the humidity. The other has to do with where people
meet. Especially leisure contacts are more likely to take place outdoors and individuals
are more likely to have windows open when the weather is nicer. To capture both channels
we allow for other contacts to have a higher seasonality than our other contact models.
Figure~\ref{fig:seasonality} shows our seasonality factors.

>>>>

% seasonality
Another important factor in the potential for a contact to lead to an infection is the
seasonality \citep{Kuehn2020} There are two channels through which
seasonality affects the infectiousness of contacts. One has to do with the physical
conditions like UV radiation and the humidity. The other has to do with where people
meet. Especially leisure contacts are more likely to take place outdoors and individuals
are more likely to have windows open when the weather is nicer. To capture both channels
we allow for other contacts to have a higher seasonality than our other contact models.
Figure~\ref{fig:seasonality} shows our seasonality factors.

### 2021-06-10 paper/report.tex
Fill in some numbers and references on policies, seasonality and from the simulation results.

The largest effect---almost one half when considering the decompositions---comes from
rapid testing. Here, it is crucial to differentiate between recorded cases and actual
cases. Additional testing means that infections become known, which would otherwise
remain undetected. Figure~\ref{fig:2021_scenarios_recorded} shows that this means that
until late April, recorded cases are higher than in the scenario where none of the three
mechanisms is turned on. Compared to the scenario with vaccinations only, this point is
reached around mid-May and it would be June for the comparison with the seasonality-only
scenario. The effect on total cases, however, is visible immediately. Despite the fact
that only a small fraction of the population performed weekly rapid tests in
March\footnote{X\% in the model; 27\% of respondents to the COSMO study reported in
    early March that they \textit{ever} did a rapid test)}\comment[id=HM]{Put in}, new
infections on April 1 would be reduced by 53\% relative to the scenario without
vaccinations, rapid tests, or seasonality.

So why is rapid testing so effective? In order to shed more light on this question,
Figure~\ref{fig:2021_scenarios_decomposition_tests} decomposes the difference in the
scenario without rapid tests only (purple line in
Figure~\ref{fig:2021_scenarios_newly_infected}) and the main specification into the
three channels for rapid tests. Tests for pupils have the smallest effect, which is
largely explained by the relatively small number of students (XXM pupils vs. YYM
workers)\comment[id=HM]{fill in} and the fact that schools did not operate at full
capacity during our period of study. Almost 40\% come from tests at the workplace.
Despite the fact that we phase rapid tests for private reasons are phased in only late,
they make up for more than half of the total effect.

\comment[id=HM]{How many tests are actually performed along each of the three dimensions? Could this be a quantity story rather than the directed testing story I am making up here as wishful thinking?}

The reason lies in the fact that a substantial share of these tests is driven by an
elevated probability to carry the virus, i.e., showing symptoms of CoViD-19 or following
up on a positive test of a household member. The latter is essentially a form of contact
tracing, which has been shown to be very effective.\comment[id=HM]{cite Priesemann
paper, others?} This is also the reason for why the number of tests performed fall at
the very end of our study period. Falling infection rates mean that there are fewer
events triggering private test demand.
\comment[id=HM]{Positive rates along the three channels might be nice here, if previous comment is not a quant story}
\comment[id=HM]{I think there is a story in here about risk conditional on past exposure vs. prospective risk in gatherings, but it is too late to work through it. We might just want to calculate the probabilities.}

>>>>

The largest effect---almost one half when considering the decompositions---comes from
rapid testing. Here, it is crucial to differentiate between recorded cases and actual
cases. Additional testing means that infections are detected, which would otherwise
remain undetected. Figure~\ref{fig:2021_scenarios_recorded} shows that this means that
until late April, recorded cases are higher than in the scenario where none of the three
mechanisms are turned on. Compared to the scenario with vaccinations only, this point is
reached around mid-May and it would be June for the comparison with the seasonality-only
scenario. The effect on total cases, however, is visible immediately. Despite the fact
that only a small fraction of the population performed weekly rapid tests in
March\footnote{8\% in the model; 27\% of respondents to the COSMO study reported in
    early March that they \textit{ever} did a rapid test)}, new
infections on April 1 would be reduced by 53\% relative to the scenario without
vaccinations, rapid tests, or seasonality.

So why is rapid testing so effective? In order to shed more light on this question,
Figure~\ref{fig:2021_scenarios_decomposition_tests} decomposes the difference in the
scenario without rapid tests only (purple line in
Figure~\ref{fig:2021_scenarios_newly_infected}) and the main specification into the three
channels for rapid tests. Tests for pupils have the smallest effect, which is largely
explained by the relatively small number of students (Only 18\% of our population are in
the education sector (pupils, teachers etc.) versus  46\% are workers outside the
education sector) and the fact that schools did not operate at full capacity during our
period of study. Almost 40\% come from tests at the workplace. Despite the fact that rapid tests for private reasons are phased in only late, they make up for more than
half of the total effect.\comment[id=HM]{How many tests are actually performed along each of the three dimensions? Could this be a quantity story rather than the directed testing story I am making up here as wishful thinking?}\comment[id=K]{This is only calculated very deeply inside the model. I'll try to save it.}

The reason lies in the fact that a substantial share of these tests is driven by an
elevated probability to carry the virus, i.e., showing symptoms of CoViD-19 or following
up on a positive test of a household member. The latter is essentially a form of contact
tracing, which has been shown to be very effective \citep{Contreras2021,
Kretzschmar2020}. This is also the reason for why the number of tests performed fall at
the very end of our study period. Falling infection rates mean that there are fewer
events triggering private test demand.
\comment[id=HM]{Positive rates along the three channels might be nice here, if previous comment is not a quant story}
\comment[id=HM]{I think there is a story in here about risk conditional on past exposure vs. prospective risk in gatherings, but it is too late to work through it. We might just want to calculate the probabilities.}
